Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
reflow
Update citations.R, manuscript.Rmd, and manuscript.md

## Introduction
Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration (Leblond et al.
2016) to avoid predators [@Bergerud_1985] and access islands during calving
(Bergerud et al. 1990). Even for adept swimmers like caribou, the
energetic expenditure of swimming for quadrupedal mammals is
significantly higher than walking or running (Fish 1993), while drowning
is also possible (Miller & Gunn 1985). Despite a large number of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean (Table 1).

>>>>

## Introduction
Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond_2016] 
to avoid predators [@Bergerud_1985] and access islands during calving
(Bergerud et al. 1990). Even for adept swimmers like caribou, the
energetic expenditure of swimming for quadrupedal mammals is
significantly higher than walking or running (Fish 1993), while drowning
is also possible (Miller & Gunn 1985). Despite a large number of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean (Table 1).
